Commit Rater

### 2015-08-25 presentations/paper/methodology.tex
Finish data extraction aside from the time table

To extract commit messages of a GitHub repository, the first and obvious attempt would be to use GitHub's API\footnote{\url{https://developer.github.com/v3/}}, which provides seemingly ideal REST resources for doing exactly that\footnote{\url{https://developer.github.com/v3/git/commits/\#get-a-commit}}. However, there is a heavy rate limit on calls to the API\footnote{\url{https://developer.github.com/v3/\#rate-limiting}}, which at the time of writing was at most 5000 requests per hour. Such a limit is only enough to analyze small repositories and is not suitable for a web application performing the rating of commits (see section\ref{sec:TODO}).

@@

\begin{table}
    \begin{tabularx}{\textwidth}{|X|X|}\hline
        \textbf{Repository} & \textbf{Time to Rate} \\\hline
        101worker & ? \\\hline
        BadgeKit & ? \\\hline
        perl & ? \\\hline
        Linux Kernel & ?\\\hline
    \end{tabularx}
    \caption{Time taken to rate commits of repositories}
    \label{tab:time}
\end{table}

Since the entirety of repository commit messages can be listed by a single call to \texttt{git log} and commits can be extracted by a single regular expression, the commit rating process is fast and scales well. Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs.

@@

% TODO: Describe extraction process
% TODO: Describe preprocessing and output
% TODO: Mention commit-limit
% TODO: Introduce example repos

>>>>

To extract commit messages of a GitHub repository, the first and obvious attempt would be to use GitHub's API\footnote{\url{https://developer.github.com/v3/}}, which provides seemingly ideal REST resources for doing exactly that\footnote{\url{https://developer.github.com/v3/git/commits/\#get-a-commit}}. However, there is a heavy rate limit on calls to the API\footnote{\url{https://developer.github.com/v3/\#rate-limiting}}, which at the time of writing was at most 5000 requests per hour. Such a limit is only enough to analyze small repositories and is not suitable for a web application performing the rating of commits (see section \ref{sec:TODO}).

@@

\begin{table}[t]
    \begin{tabularx}{\textwidth}{@{}|Y|Y|@{}}\hline
        \textbf{Repository} & \textbf{Time to Rate} \\\hline
        101worker & 10 seconds \\\hline
        BadgeKit & 4 seconds \\\hline
        perl & ? \\\hline
        Linux Kernel & ?\\\hline
    \end{tabularx}
    \caption{Time taken to clone repositories and rate their commits}
    \label{tab:time}
\end{table}

Since the entirety of repository commit messages can be listed by a single call to \texttt{git log} and commits can be extracted by a single regular expression, the commit rating process is fast and scales well. Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs. The actual time taken to rate these repositories on the server the application is running on are found in table \ref{tab:time}.

However, to keep the prototype website usable for multiple users at once, we decided to limit the number of commits analyzed to the latest $10,000$ commits. However, this practical limit may be increased by allowing more worker processes to rate repositories at once, reducing the chance of the entire commit rater being blocked for a long time by large repositories.

@@
